Misc Code

### 2019-04-16 Data Preparation.Rmd

  left_join(map_assessment_AoD, by = "Assessment") %T>%

@@

@@

@@

  # for simplicity, we only keep 
  # *UCM courses*  (courses present in the UCM catalogue)
  # taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (Program (Abbreviation) = 7501)

  filter(
    `Module (Abbrev.)` %>% is_UCM,
    `Program (Abbreviation)` == "7501"
    ) %>%

@@

```{r d_transcript column selection}
d_transcript <- d_transcript %>%

  # Remove variables with only one value (~10)
  discard(function(x) n_distinct(x) == 1) %>%

  # Select: Student ID, course ID, when a course is taken and the grade 
  select(
    `Student ID`   = `Student Number`,
    `Course ID`    = `Module (Abbrev.)`,
    Year_numerical = `Academic Year`,
    Period         = `Academic Session`,
    Grade          = `Grade symbol`
    )
```

@@

  if(is.na(grade) | grade == "NG") grade <- "0"

@@

    # Combine year and period to have be able to order the course in time using a single variable
    time = str_c(Year_numerical, period_numerical) %>% as.numeric,

@@

@@

```{r}
d_transcript_elective <- d_transcript_augmented %>%
  filter(`Course ID` %>% is_elective) %>%
  select(`Student ID`, `Course ID`, time, Grade, grade_ceil)
```

@@

@@

save(d_transcript_augmented, d_transcript_elective, file = "Output/data_pillar_1.RDATA")

>>>>

  left_join(map_assessment_AoD, by = "Assessment") %>%

  filter(!is.na(AoD)) %T>%

@@

##
```{r}
d_course <- d_course %>%
  mutate(target = Number > 2000 & Type == "Elective" & (! str_detect(`Course ID`, "SA")))
```

@@

The data set `d_transcript` contains both the failed grades and the grade of the resit, and does not distinguish between them (same student, same course, same yera, same period, but different grade).

@@

  # for simplicity, we only keep 
  # courses taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (Program (Abbreviation) = 7501)

  filter(`Program (Abbreviation)` == "7501") %>%

@@

```{r d_transcript column selection}
d_transcript <- d_transcript %>%
  # keep variables: Student ID, course ID, when a course is taken and the grade 
  select(
    `Student ID`   = `Student Number`,
    `Course ID`    = `Module (Abbrev.)`,
    Year_numerical = `Academic Year`,
    Period         = `Academic Session`,
    Grade          = `Grade symbol`
    )
```

@@

  if(grade == "NG" | is.na(grade)) return(NA)

@@

    # Combine year & period to chronologically order courses using a single variable
    time = str_c(Year_numerical, period_numerical) %>% as.numeric,

@@

```{r}
d_transcript <- d_transcript %>% filter(!is.na(Grade))
```

@@

@@

  # ~ 10 incomplete rows for a student's profile
  d_transcript %>% filter(`Student ID` == "0481343") %>% View

@@

save(d_transcript_augmented, file = "Output/data_pillar_1.RDATA")

### 2019-04-16 Misc Code.Rmd

>>>>

## CV

```{r my_predict, eval = F}
my_predict <- function(model, newdata, id){

  df    <- as.matrix(newdata)
  coefi <- coef(model, id = id)
  xvars <- names(coefi)[-1]

  coefi[1] + df[ , xvars, drop = FALSE] %*% coefi[-1]

```{r my_CV, eval = F}
my_CV <- function(df){

  k <- 10
  set.seed(2019)
  folds <- sample( 1 : k, nrow(df), replace = TRUE)

  nvmax <- 5
  cv.errors <- matrix(NA, k, nvmax, dimnames = list(NULL, paste(1 : nvmax, "predictor(s)")))

  for(j in 1 : k){

    training <- df[folds != j, ]
    test     <- df[folds == j, ]

    m <- regsubsets(Grade ~ ., data = training, nvmax = nvmax)

    for(i in 1 : nvmax){

      pred            <- my_predict(model = m, newdata = test, id = i)
      pred            <- pmin(10, pred)
      pred            <- pmax(0, pred)
      cv.errors[j, i] <- mean(abs(test$Grade - as.vector(pred)))

    }

  }

  cv.errors

## BSS
```{r my_BSS, eval = F}
my_BSS <- function(df) regsubsets(Grade ~ ., data = df, nvmax = 7)
```

```{r extract_coef, eval = F}
extract_coef <- function(BSS, BS) names(coef(BSS, BS))[-1]
```

```{r my_lm, eval = F}
my_lm <- function(df, best_coef){

  best_coef %>%

    paste0(collapse = " + ") %>%
    paste0("Grade ~ ", .) %>%
    as.formula %>%

    lm(data = df)

```{r model fitting, eval = F}
BSS <- tibble(target = course_obj) %>%

  mutate(df = target %>% map(find_df),
         n = df %>% map(nrow)) %>%

  filter(n >= 25) %>%

  mutate(BSS = df %>% map(my_BSS)) %>%

  mutate(CV_error      = df %>% map(my_CV),
         CV_error_mean = CV_error %>% map(colMeans),
         n_pred        = CV_error_mean %>% map_dbl(which.min),
         best_coef     = list(BSS, n_pred) %>% pmap(extract_coef),
         best_model    = list(df, best_coef) %>% pmap(my_lm)
         ) %>%

  mutate(tidied    = best_model %>% map(broom::tidy   ),
         glanced   = best_model %>% map(broom::glance ),
         augmented = best_model %>% map(broom::augment)) %>%

  select(target, n, tidied, glanced, augmented)
```

```{r, eval = F}
BSS_glance <- BSS %>% unnest(glanced) %>% select(-c(tidied, augmented)) %>%

  mutate(MSE = deviance / df.residual )

View(BSS_glance)
```

```{r, eval = F}
course <- "HUM2021"

BSS_tidy_temp <- BSS %>% filter(target == course) %>% unnest(tidied, .drop = F) %>% select(-c(glanced, augmented))

View(BSS_tidy_temp)

BSS_augm_temp <- BSS %>% filter(target == course) %>% unnest(augmented, .drop = FALSE) %>% select(-c(tidied, glanced))

View(BSS_augm_temp)
```
